Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-05-07 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Filling in missing parts of draft

  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the figures
  that follow, we graphically illustrate the procedure which is described in detail in
  Section~\ref{M-method:IHMM} of the main text.

  \begin{enumerate}
  	\item Parameterize in $x$, $y$, $z$ coordinates with $x$, $y$ coordinates relative to the nearest
  	pore center (see Figure~\ref{fig:xyz_hmm}). 	
  	\item Convert $x$ and y coordinates to radial coordinates, $r$, then fix the state sequence
  	and use the inference component of the IHMM in order to estimate the parameters in terms
  	of $r$ and $z$ (see Figure~\ref{fig:rz_hmm}). 	 	
  	\item Cluster the VAR parameters from the states found in all 24 trajectories. Reassign the state
  	sequence so that segments which belong to the same cluster are labeled the same across all solute
  	trajectories.
  	\item Subtract the mean of each segment, obtained before clustering, in order to zero out the
  	trajectory.
  	\item Fix clustered state sequence and infer parameters of each state, assuming a mean of zero
  	for all states (see Figure~\ref{fig:zeroed_hmm}). 
  \end{enumerate}

@@

  \section{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}

@@

  \section{Choosing the Number of Clusters}\label{section:nclusters}

>>>>

@@

  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the steps and
  figures that follow, we graphically illustrate the procedure which is described in detail 
  in Section~\ref{M-method:IHMM} of the main text.

  \begin{enumerate}
  	\item Parameterize in $x$, $y$, $z$ coordinates with $x$, $y$ coordinates relative to the nearest
  	pore center (see Figure~\ref{fig:xyz_hmm}). 	
  	\item Convert $x$ and $y$ coordinates to radial coordinates, $r$, then fix the state sequence
  	and use the inference component of the IHMM in order to estimate the parameters in terms
  	of $r$ and $z$ (see Figure~\ref{fig:rz_hmm}). 	 	
  	\item Cluster the VAR parameters from the states found in all 24 trajectories. Reassign the state
  	sequence so that segments which belong to the same cluster are labeled the same across all solute
  	trajectories.
  	\item Subtract the mean of each segment, obtained before clustering, in order to zero out the
  	trajectory.
  	\item Fix clustered state sequence and infer parameters of each state, assuming a mean of zero
  	for all states (see Figure~\ref{fig:zeroed_hmm}). 
  \end{enumerate}

  \section{Clustering}\label{section:clustering}

  \subsection{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}

@@

  \subsection{Clustering on the self-transition probabilities}\label{section:selfT_cluster}

  To cluster on $T_{ii}$, we first
  cast it in terms of the expected dwell times. The expected value of the number of sequential
  self-transitions is simply $\frac{1}{1 - T_{ii}}$. This relationship correctly implies that 
  dwell times approach infinity as $T_{ii}$ approaches 1. There we found the most success with
  agglomerative clustering by linearizing this relationship and clustering on $-log(1 - T_{ii})$.

  \subsection{Choosing the Number of Clusters}\label{section:nclusters}

### 2020-05-07 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Filling in missing parts of draft

  Mathematically modeling complex transport phenomena can be a powerful tool
  for extracting important physical information from molecular simulations. 
  In this study, we present two new approaches that use stochastic time series
  modeling to predict long time-scale behavior and macroscopic properties 
  from molecular simulation which can be generalized to other molecular systems
  where complex diffusion occurs. Specifically, we parameterize our models using
  long molecular dynamics (MD) simulation trajectories of a cross-linked 
  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
  predict solute mean squared displacements (MSDs) and solute flux, and thus 
  solute selectivity, in macroscopic length pores.

@@

  Highly selective separations membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} 
  %BJCB: could cut this last sentence. It's kind of awkward  
  %MRSB: agree  
  %In the materials industry, there is a strong interest in creating breathable
  %fabrics which selectively allow passage of water
  %vapor.~\cite{mondloch_destruction_2015}

@@

  % BJCB: split into two paragraphs  
  In this work, we study the inverted hexagonal, H\textsubscript{II}, LLC phase. 
  The H\textsubscript{II} phase has densely packed, uniform-sized pores on the 
  order of 1 nm in size. A perfectly aligned H\textsubscript{II} phase has 
  an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}
  %BJCB: could add a sentence saying that in pracftice, alignment is hard. Not sure if worth acknowledging for this paper.
  %MRSB: nah, not here.

@@

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. We chose to study the
  H\textsubscript{II} phase because it is a simpler geometry to model than the
  Q\textsubscript{I} phase and significantly more structural data is available
  to help ensure molecular models are consistent with experiment. In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

@@

  We fit sFBM models in two ways: First, we parameterize solute motion using
  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
  Second, we use a two-state approach by extracting two sets of model parameters
  calculated based on a solute's radial distance from the closest pore center. 
  This allows us to include the different dynamical behavior of solutes previously
  observed within the pore region versus within the monomer tails.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an
  atomistic molecular model of four pores in a monoclinic unit cell with 10\%
  water by weight (see Figure~\ref{fig:membrane_structure}). Approximately one
  third of the water molecules occupy the tail region with the rest near the
  pore center. We chose to focus our study on the 10 wt\% water system because
  solutes move significantly faster than in the 5 wt\% system studied
  previously, thus allowing more statistically valid analyses.

@@

  sFBM implies that hops are correlated which we describe using the Hurst
  parameter, $H$. The autocovariance function of hop lengths has the
  analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from
  which hops are drawn and $k$ is the time lag, or number of increments between
  hops. The hop autocorrelation function is simply
  Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance.  When $H <
  0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian
  motion and when $H > 0.5$, one observes positive correlation between hops.

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
  length distributions result in rare but arbitrarily long hops. These long and
  unrealistic hops result in over-estimated simulated MSDs (see
  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
  distribution of hops observed in our MD simulations are well approximated by
  L\'evy stable distributions close to the mean, but they significantly
  under-sample the tails. We chose to truncate the L\'evy stable distributions
  based on where the theoretical probability distribution function (PDF) starts
  to deviate from the empirically measured PDF (see
  Section~\ref{S-section:truncation} of the Supporting Information).~\cite{mantegna_stochastic_1994}

@@

  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  We find the data suggests that solute motion in this system can be
  well-modeled by subordinated fractional Brownian motion. In
  Figure~\ref{fig:solute_trajectories}, we plotted representative trajectories
  for each solute. They are characterized by intermittent hops between periods
  of entrapment. The near-Gaussian distribution of jump lengths and power law
  distribution of dwell times are both characteristic of CTRWs
  (See Figures~\ref{S-fig:hop_distribution_comparison} and~\ref{S-fig:powerlaw}
  of the Supporting Information). 
  %The apparent
  Anti-correlation between hops suggests a fractional diffusion process is 
  subordinate to the CTRW. Of the different models, a process subordinated by 
  FBM or FLM is best supported by the data because the analytical correlation 
  structures of hop lengths are close to those observed in our simulations 
  (See Figure~\ref{S-fig:hop_acf} of the Supporting Information). Fractional 
  motion is common in crowded viscoelastic environments where motion is highly
  influenced by the movement of surrounding components, such as monomer tails 
  in our case.~\cite{ernst_fractional_2012}

@@

  We modeled the distributions of hop lengths in two ways. First, we assumed
  the distribution to be Gaussian since it is possible to exactly simulate
  realizations of fractional Brownian motion. Second, we fit the distributions
  to L\'evy stable distributions since it is more general than the Gaussian
  distribution. We plotted the MLE fits of both on top of urea's hop length
  distribution in Figure~\ref{S-fig:hop_distribution_comparison} of the
  Supporting Information. The L\'evy distribution does a better job capturing
  the somewhat heavy tails and high density near 0 of the hop length distribution. 
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, this more general fit may not be 
  worthwhile. In fact, we typically observe very little difference between model
  predictions parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).

  We also modeled the distribution of dwell times in two ways. First, we
  assumed pure power law behavior since it is consistent with most theoretical
  descriptions of CTRWs. The data fits well to this model at short dwell times
  but the density of long dwell times is over-estimated. In our second
  approach, we truncate the power law distribution with an exponential cut-off,
  lowering the probability of extremely long dwell times. 
  %We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where 
  On long time scales, the density of the truncated power law drops below that
  of the pure power law and tends towards 0 near a dwell time of 250 ns.

@@

  % BJCB: I'm not sure I want to move this paragraph because I think the curvature
  % is important to discuss and I mention its implications in the conclusion
  The deviation between the one mode MSD predictions and MD are primarily due
  to differences in their curvature at long time lags. The shape and magnitude
  of the predicted curves appears accurate relative to MD at short time lags.
  However, the modeled trajectories undershoot the mean MD MSD as the time lag
  increases. Long time positional anti-correlation, on the order of hundreds of
  ns, may not exist in the MD system. Eventual loss of correlation would result 
  in a shift from sub-linear to linear MSD behavior, as observed in the MD 
  trajectories. Acetic acid exemplifies this point. At first glance, acetic acid's
  predicted MSD appears to match the curvature of MD quite well, but closer 
  examination reveals that
  the MD MSD curve may actually shift from a sub-linear to a linear regime around
  500 ns.

@@

  \item \textit{Methanol} spends most of its time unbound in the tail region (state 1) and
  spends a significant portion of time hydrogen bonded while in the tail
  region. Tail region hydrogen bonds are donated from methanol to the ether
  linkages between the monomer head groups and tails. One might modify the
  rate of methanol transport by controlling its partition into the monomer
  tails. This might be achieved by adding cross-linkable groups near the
  monomer head groups.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_ad}
  \end{subfigure}
  \caption{(a) The distributions of first passage times generated from the
	  sFBMcut model fit well to Equation~\ref{eqn:passage_times}. We show
	  similar fits for the remaining solutes in
	  Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The
	  single particle flux measured by the sFBMcut AD model decays with
	  increasing pore length. The rankings of solute fluxes are consistent
	  with the MSDs predicted by each model. We fit the single particle
	  solute flux versus pore length, $L$, to a power law function of the
	  form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
  }\label{fig:flux_curves}
  \end{figure}

  The scaling of solute flux with pore length is primarily influenced by
  anti-correlation between solute hops. In Figure~\ref{fig:beta}a, we show that
  $\beta$ is inversely related to the Hurst parameter. This makes intuitive
  sense since higher degrees of anti-correlation should slow the rate at which
  solutes cross the membrane pore. When we remove anti-correlation between
  hops (set $H$=0.5), the length dependence becomes the same for all solutes,
  dropping to a value just below 2. This also implies that hop lengths and
  dwell times do not affect length dependence since each solute exhibits
  different hopping and trapping behavior yet are all parameterized by the same
  value of $\beta$ when $H$=0.5. We further verified this claim by removing
  hop anti-correlation and setting all dwell times equal to one timestep,
  effectively simulating Brownian motion.  The length dependence remains
  unchanged.

>>>>

  Mathematically modeling complex transport phenomena can be a powerful tool
  for extracting important physical information from molecular simulations. 
  In this study, we present two new approaches that use stochastic time series
  modeling to predict long time-scale behavior and macroscopic properties 
  from molecular simulation which can be generalized to other molecular systems
  where complex diffusion occurs. Specifically, we parameterize our models using
  long molecular dynamics (MD) simulation trajectories of a cross-linked 
  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
  predict solute mean squared displacements (MSDs), solute flux, and
  solute selectivity in macroscopic length pores.

@@

  Highly selective separation membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} 
  %BJCB: could cut this last sentence. It's kind of awkward  
  %MRSB: agree  
  %In the materials industry, there is a strong interest in creating breathable
  %fabrics which selectively allow passage of water
  %vapor.~\cite{mondloch_destruction_2015}

@@

  % BJCB: split into two paragraphs  
  In this work, we study the inverted hexagonal, H\textsubscript{II}, LLC phase. 
  The H\textsubscript{II} phase has densely packed, uniform-sized pores on the 
  order of 1 nm in size. A perfectly aligned H\textsubscript{II} phase has 
  an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}

@@

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. 
  %We chose to study the
  %H\textsubscript{II} phase because it is a simpler geometry to model than the
  %Q\textsubscript{I} phase and significantly more structural data is available
  %to help ensure molecular models are consistent with experiment. 
  In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

@@

% BJCC: I cut this, doesn't really seem to be necessary for intro
%  We fit sFBM models in two ways: First, we parameterize solute motion using
%  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
%  Second, we use a two-state approach by extracting two sets of model parameters
%  calculated based on a solute's radial distance from the closest pore center. 
%  This allows us to include the different dynamical behavior of solutes previously
%  observed within the pore region versus within the monomer tails.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an
  atomistic molecular model of four pores in a monoclinic unit cell with 10\%
  water by weight (see Figure~\ref{fig:membrane_structure}). Approximately one
  third of the water molecules occupy the tail region with the rest near the
  pore center.
%BJCC: I don't see a need to justify 10 over 5 wt% 
%  We chose to focus our study on the 10 wt\% water system because
%  solutes move significantly faster than in the 5 wt\% system studied
%  previously, thus allowing more statistically valid analyses.

@@

  sFBM implies that hops are correlated which we describe using the Hurst
  parameter, $H$. The autocovariance function of hop lengths has the
  analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from
  which hops are drawn and $k$ is the time lag, or number of increments between
  hops. The hop autocorrelation function is simply
  Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance.  When $H <
  0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian
  motion and when $H > 0.5$, one observes positive correlation between hops. 
  We obtained $H$ by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first ten 0.5 ns time lags of 
  the empirically measured autocorrelation function (see section~\ref{S-section:H_estimate}
  of the Supporting Information for a more in depth justification of this method).

% BJCC: left this discussion for supporting. Added last sentence above
%  There are many methods for estimating the Hurst parameter for a time series.
%  \cite{clegg_practical_2006} It can be a difficult task because 
%  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
%  $H > 0.5$, meaning one needs to study large time lags with high frequency.
%  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
%  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
%  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
%  fitting longer time lags to our data is lost in the noise since the analytical values
%  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
%  Equation~\ref{eqn:fbm_autocorrelation} to the first 
%  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
  length distributions result in rare but arbitrarily long hops. These long and
  unrealistic hops result in over-estimated simulated MSDs (see
  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
  distribution of hops observed in our MD simulations are well approximated by
  L\'evy stable distributions close to the mean, but they significantly
  under-sample the tails. We chose to truncate the L\'evy stable distributions
  based on where the theoretical PDF starts
  to deviate from the empirically measured PDF (see
  Section~\ref{S-section:truncation} of the Supporting Information).~\cite{mantegna_stochastic_1994}

@@

  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~Hop Length Distribution~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  We find the data suggests that solute motion in this system can be
  well-modeled by subordinated fractional Brownian motion. In
  Figure~\ref{fig:solute_trajectories}, we plotted representative trajectories
  for each solute. They are characterized by intermittent hops between periods
  of entrapment. The near-Gaussian distribution of jump lengths and power law
  distribution of dwell times are both characteristic of CTRWs
  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). 
  %The apparent
  Anti-correlation between hops suggests a fractional diffusion process is 
  subordinate to the CTRW. Of the different models, a process subordinated by 
  FBM or FLM is best supported by the data because the analytical correlation 
  structures of hop lengths are close to those observed in our simulations 
  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). Fractional 
  motion is common in crowded viscoelastic environments where motion is highly
  influenced by the movement of surrounding components, such as monomer tails 
  in our case.~\cite{ernst_fractional_2012}

@@

  We modeled the distributions of hop lengths in two ways. First, we assumed
  the distribution to be Gaussian since it is possible to exactly simulate
  realizations of fractional Brownian motion. Second, we fit the distributions
  to L\'evy stable distributions since it is more general than the Gaussian
  distribution. We plotted the MLE fits of both on top of each solute's hop length
  distribution in Figure~\ref{S-fig:anticorrelated_hops} of the
  Supporting Information. The L\'evy distribution does a better job capturing
  the somewhat heavy tails and high density near 0 of the hop length distributions. 
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, this more general fit may not be 
  worthwhile. In fact, we typically observe very little difference between model
  predictions parameterized with FLM versus FBM.% (see Figure~\ref{fig:anomalous_msds}).

  We also modeled the distribution of dwell times in two ways. First, we
  assumed pure power law behavior since it is consistent with most theoretical
  descriptions of CTRWs. The data fits well to this model at short dwell times
  but the density of long dwell times is over-estimated. In our second
  approach, we truncate the power law distribution with an exponential cut-off,
  lowering the probability of extremely long dwell times. 
  %We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where 
  On long time scales, the density of the truncated power law drops below that
  of the pure power law and tends towards 0. % near a dwell time of 250 ns.

@@

  % BJCB: I'm not sure I want to move this paragraph because I think the curvature
  % is important to discuss and I mention its implications in the conclusion
  The deviation between the one mode MSD predictions and MD are primarily due
  to differences in their curvature at long time lags. The shape and magnitude
  of the predicted curves appears accurate relative to MD at short time lags.
  However, the modeled trajectories undershoot the mean MD MSD as the time lag
  increases. Long time positional anti-correlation, on the order of hundreds of
  ns, may not exist in the MD system. Eventual loss of correlation would result 
  in a shift from sub-linear, or subdiffusive, to linear, or diffusive, MSD behavior, as observed in the MD 
  trajectories. Acetic acid exemplifies this point. At first glance, acetic acid's
  predicted MSD appears to match the curvature of MD quite well, but closer 
  examination reveals that
  the MD MSD curve may actually shift from a sub-linear to a linear regime around
  500 ns.

@@

  \item \textit{Methanol} spends most of its time unbound in the tail region (state 1) and
  spends a significant portion of time hydrogen bonded while in the tail
  region. Tail region hydrogen bonds are donated from methanol to the ether
  linkages between the monomer head groups and tails, as well as to the ester groups
  at the ends of the tails. One might modify the
  rate of methanol transport by controlling its partition into the monomer
  tails. This might be achieved by adding cross-linkable groups near the
  monomer head groups.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_ad}
  \end{subfigure}
  \caption{(a) The distributions of first passage times generated from the
	  sFBMcut model fit well to Equation~\ref{eqn:passage_times}. We show
	  similar fits for the remaining solutes in
	  Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The
	  single particle flux measured by the sFBMcut AD model decays with
	  increasing pore length. The rankings of solute fluxes are consistent
	  with the MSDs predicted by each model. We fit the single particle
	  solute flux versus pore length, $L$, to a power law function of the
	  form $AL^{-\beta}$ (dashed lines). 
  }\label{fig:flux_curves}
  \end{figure}

  The scaling of solute flux with pore length is primarily influenced by
  anti-correlation between solute hops. In Figure~\ref{fig:beta}a, we show that
  $\beta$ is inversely related to the Hurst parameter. This makes intuitive
  sense since higher degrees of anti-correlation should slow the rate at which
  solutes cross a membrane pore of a given length. When we remove anti-correlation between
  hops (set $H$=0.5), the length dependence becomes the same for all solutes,
  dropping to a value just below 2. This also implies that hop lengths and
  dwell times do not affect length dependence since each solute exhibits
  different hopping and trapping behavior yet are all parameterized by the same
  value of $\beta$ when $H$=0.5. We further verified this claim by removing
  hop anti-correlation and setting all dwell times equal to one timestep,
  effectively simulating Brownian motion.  The length dependence remains
  unchanged.
